Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-20 journal/article.tex
Success: Customizing

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        \toprule
        Challenges in requirements engineering and quality assurance  &  Described in \\
        \midrule
        How to accommodate high level requirements management  &  P24, P31, P39, P45  \\
        Problems with breakdown of requirements        &  P1, P17, P33, P48  \\
        Creating and estimating user stories is hard   &  P5, P11, P27, P30, P33, P37 \\
        Handling coexisting long and short term planning  &  P9, P10, P13, P26, P31, P38 \\
        Accommodating performance, load, and memory testing  &  P17, P28, P31, P48 \\
        Lack of automated testing slows down           &  P10, P11, P17 \\
        New requirements management practices affect QA  &  P5, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of requirements engineering and quality assurance related
             challenges relating in the agile model}
    \label{table:challenges_requirementsandqa}
\end{table}

@@

Requirements were in some cases first defined on a high level in marketing
requirements documents (MRD) [P1, P31] or functional specifications [P33].
These high level requirements needed to be elaborated to be used by agile
development teams. The requirements breakdown in it self was found to be
difficult [P1, P33], and also when to do the breakdown and to which detail level
[P17].
Product managers and business analysts were struggling in creating high level
requirements [P33, P37], and teams were struggling in breaking them down to an
estimable size [P33]. Smits and Rilliet [P48] describe how high level product
management delivered requirements in too large chunks resulting in development
teams spending large amounts of time on defining suitably sized stories.

@@

One advice given by few cases was to keep the organization simple. Beavers [P5]
describes that attempting to operate in a complex and global setting complicated
even simple agile practices. The organizational chart was simplified, which was
welcomed by both employees and managers [P5]. Rather than focusing on detail in
process, communication practices, and tools the focus should be on engaging the
teams [P40].

@@

@@

@@

>>>>

-- Who will be interested of this?

-- What can be learned from this`?

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        \toprule
        Challenges in requirements engineering and quality assurance  &  Described in \\
        \midrule
        How to accommodate high level requirements management  &  P24, P31, P39, P45, P51  \\
        Problems with breakdown of requirements        &  P1, P17, P33, P48  \\
        Creating and estimating user stories is hard   &  P5, P11, P27, P30, P33, P37 \\
        Handling coexisting long and short term planning  &  P9, P10, P13, P26, P31, P38 \\
        Accommodating performance, load, and memory testing  &  P17, P28, P31, P48 \\
        Lack of automated testing slows down           &  P10, P11, P17 \\
        New requirements management practices affect QA  &  P5, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of requirements engineering and quality assurance related
             challenges relating in the agile model}
    \label{table:challenges_requirementsandqa}
\end{table}

@@

Requirements were in some cases first defined on a high level in marketing
requirements documents (MRD) [P1, P31] or functional specifications [P33].
These high level requirements needed to be elaborated to be used by agile
development teams. The requirements breakdown in it self was found to be
difficult [P1, P33], and also when to do the breakdown and to which detail level
[P17].
Product managers and business analysts were struggling in creating high level
requirements [P33, P37, P51], and teams were struggling in breaking them down to an
estimable size [P33]. Smits and Rilliet [P48] describe how high level product
management delivered requirements in too large chunks resulting in development
teams spending large amounts of time on defining suitably sized stories.

@@

One advice given by few cases was to keep the organization and process simple
[P10, P16]. Beavers [P5] describes that attempting to operate in a complex and
global setting complicated even simple agile practices. The organizational chart
was simplified, which was welcomed by both employees and managers [P5]. Rather
than focusing on detail in process, communication practices, and tools the focus
should be on engaging the teams [P40].

@@

% Customizing the agile model

Customizing the agile model and practices was reported as an necessary step in
the agile implementation. As each organization will have its own challenges in
adopting agile, it should be carefully considered which organization specific
areas to focus on when choosing the agile practices to implement  [P8, P43].
Lewis and Nehrer [P29] recommended to choose the agile model according to the
current corporate model in order to avoid interference.

Especially in a large organization it is not feasible to use the same process
for all projects [P49]. An individual application of the agile process is needed
for different types of development, depending on for instance the type of
software being developed or the project size [P45].
Applying agile at scale will require to deviate from some of the typical
recommendations [P31]. However, it is essential to remember the agile principles
when doing customizations, and watch out for customization that contradict with
the principles [P31].

Cases reported that customization was part of a successful agile implementation.
For instance, teams were let to customize their practices individually, to fit
the needs of each team [P41].
Spayd [P49] writes that teams who modified agile practices to suite te large and
distributed environment ended up doing better than teams that did not.
% Some intermediate point?
To allow teams to become innovative and perform well the agile model should be
customized in a pragmatical way instead of following a strict textbook
interpretation [P10]

The customization of the agile model was also seen as an evolutionary process.
Cowan [11] suggested that in a big-bang transformation it might be necessary to
selectively compromise some parts of the agile implementation so that the core
practices can be set in place.
The agile transformation is a constantly ongoing process, and it is recommended
to regularly challenge teams to refine the agile implementation to reflect the
courrent needs of the organization [P41, P43].

% Customize the agile model?
% ??
% [P16]
% This cross-functional team redesigned and rebuilt the development process from
% the ground up using key values from the company’s founding: KISS (Keep it Simple
% Stupid), iterate quickly, and listen to our customers. These values are a
% natural match for agile methodologies.
% 
% ??? There are changes done to the agile proces, but doing it is not that much emphasized
% [P51]
% One after the other, all products where then switched to the new Scrum process.
% Along the way, minor adjustments were often made. The teams were constantly
% searching for the right balance between sprint duration, size estimation,
% requirement size, and time spent on backlog administration. Changes to the
% process were initially often managed by the the CTO. However, they were
% increasingly delegated to the appropriate ScrumMasters.
% Comment: This is not directly seen as a success factor.

@@

* Some success factors and challenges are ``symmetrical'', so that lack of some
  factor is a challenge, but availability of it provides success

@@

* Customization of practices was seen as necessary, as large scale has demands
  over the original agile ideas
